Automated data-driven symbolic modeling of the lift forces acting on flapping wings

### 2021-02-01 paper/main.tex
Add color package
Add highlighted notes
Move highlighted comments to TODOs in the .tex file
Replace Whitney-Wood and Pesavento-Want with initials and references

\documentclass{article}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{authblk}
\usepackage{fullpage}

@@

% % See https://tex.stackexchange.com/questions/286737/sub-figures-of-different-sizes-grid-layout
\begin{figure}%[!htb]
\centering
\begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[height=5cm]{figures/apparatus2}
    \caption{\label{fig:apparatus2}}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[height=5cm]{figures/apparatus3}
    \caption{\label{fig:apparatus3}}
\end{subfigure}
\caption{\subref{fig:apparatus2} Front view of the flapping wing apparatus
  showing the wing mounted on its driving mechanism attached to the force
  sensor. \subref{fig:apparatus3} Close-up view of the 3D printed frame and
  crank mechanism used to drive the flapping motion of the wing.}
\end{figure}

\subsection*{High-speed measurement of flapping kinematics}
A Casio EXILIM EX-FH20 color video camera was used to record each experiment at
210 frames per second from a top-down perspective as well as a side view
provided by a mirror mounted in the field of view.  The main beam of each wing
was colored red to enable precise tracking of the stroke angle.  The top-down
projected area of the wing was used to extract deflection angle, and tracking of
the wing tip in the side-view was used to extract the angle of deviation out of
the wing's stroke plane.  These three angles precisely define the configuration
of the wing.  A schematic diagram of this apparatus is shown in
Figure~\ref{fig:apparatus}. A variety of image-processing techniques were used
to extract the kinematics of the wing motion from high-speed video.  The
red-colored main beam was identified with a color filter and a line was fitted
using a Hough Transform to identify the stroke angle.  The wing deflection angle
was computed by measuring the projected area of the wing in the image and
compared with the known dimensions of the rectangular wing shape. The
out-of-plane deviation angle of the wing was measured by tracking the leading
and trailing edge corners of the wingtip in the side-view of the mirror. We
refer the reader to our previous work for a more detailed description of our
methods of extracting wing kinematics from high speed video and processing the
measured data\cite{richter2012thesis}.
% Figure~\ref{fig:kinematics} provides sample force data and measured wing
% kinematics from one experiment.

@@

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|r|r|r|}
\hline
  {\bf Model} & {\bf Terms/Formula} & {\bf Size} & {\bf MAE (N)}\\
\hline
\(EQ _5\) & \(C_1RY_{CM}\dot{\psi}^2\ + C_2RX_{CM}\dot{\phi}\psi - C_3R\ddot{\theta}\) & 12 & 1.19\e{-3}\\
\(EQ _4\) & \(C_1RY_{CM}\dot{\psi}^2\cos\psi + C_2RX_{CM}\dot{\phi}\psi - C_3R\ddot{\theta}\) & 14 & 1.18\e{-3}\\
\(EQ _3\) & \(C_1RY_{CM}\dot{\psi}^2\cos(\psi-\psi^2) + C_2RX_{CM}\dot{\phi}\psi - C_3R\ddot{\theta}\) & 16 & 1.14\e{-3}\\
\(EQ _2\) & \(C_1RY_{CM}\dot{\psi}^2\cos\psi + C_2RX_{CM}\dot{\phi}\psi - C_3R\dot{\phi}\dot{\psi}\psi - C_4R\ddot{\theta}\) & 19 & 1.14\e{-3}\\
\(EQ _1\) & \(C_1RY_{CM}\dot{\psi}^2\cos\psi + C_2RX_{CM}\dot{\phi}\psi - C_3R\ddot{\theta}\dot{\phi}\psi - C_4R\dot{\phi}\dot{\psi}\psi - C_5R\ddot{\theta}\) & 24 & 1.12\e{-3}\\
\hline
\(U^2\) Planar 1 & \(L_{planar},  F_{inertial\:(pendulum\:only)}\) & 32 & 1.46\e{-3}\\
\(U^2\) Planar 2 & \(L_{planar}, F_{inertial}\) & 46 & 1.28\e{-3}\\
\(U^2\) Total & \(L_{trans}, F_{inertial}\) & 96 & 1.28\e{-3}\\
Whitney-Wood & \(L_{trans}, AM_{trans}, AM_{rot}\) & 121 & 1.21\e{-3}\\
Pesavento-Wang & \(L_{trans}, L_{rot}, AM_{trans}, AM_{trans-rot}\) & 130 & 1.20\e{-3}\\
\hline
\end{tabular}
\caption{\label{table:eqmodels}Comparison of data-driven models and analytical
  equations of lift.  The models are sorted by equation size, which is
  calculated as the sum of arithmetic and trigonometric operators required to
  compute a force prediction from kinematic and geometric data.  MAE reports
  average mean absolute error (in Newtons of vertical force) for the ten test
  experiments.}
\end{table}

@@

\bibliographystyle{abbrv}
\bibliography{main}

>>>>

\documentclass{article}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{authblk}
\usepackage{fullpage}
\usepackage{color}

@@

% TODO: Mention empirically measuring impulse response.

% See https://tex.stackexchange.com/questions/286737/sub-figures-of-different-sizes-grid-layout
\begin{figure}%[!htb]
\centering
\begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[height=5cm]{figures/apparatus2}
    \caption{\label{fig:apparatus2}}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
    \centering
    \includegraphics[height=5cm]{figures/apparatus3}
    \caption{\label{fig:apparatus3}}
\end{subfigure}
\caption{\subref{fig:apparatus2} Front view of the flapping wing apparatus
  showing the wing mounted on its driving mechanism attached to the force
  sensor. \subref{fig:apparatus3} Close-up view of the 3D printed frame and
  crank mechanism used to drive the flapping motion of the wing.}
\end{figure}

\subsection*{High-speed measurement of flapping kinematics}
A Casio EXILIM EX-FH20 color video camera was used to record each experiment at
210 frames per second from a top-down perspective as well as a side view
provided by a mirror mounted in the field of view.  The main beam of each wing
was colored red to enable precise tracking of the stroke angle.  The top-down
projected area of the wing was used to extract deflection angle, and tracking of
the wing tip in the side-view was used to extract the angle of deviation out of
the wing's stroke plane.  These three angles precisely define the configuration
of the wing.  A schematic diagram of this apparatus is shown in
Figure~\ref{fig:apparatus}. A variety of image-processing techniques were used
to extract the kinematics of the wing motion from high-speed video.  The
red-colored main beam was identified with a color filter and a line was fitted
using a Hough Transform to identify the stroke angle.  The wing deflection angle
was computed by measuring the projected area of the wing in the image and
compared with the known dimensions of the rectangular wing shape. The
out-of-plane deviation angle of the wing was measured by tracking the leading
and trailing edge corners of the wingtip in the side-view of the mirror. We
refer the reader to our previous work for a more detailed description of our
methods of extracting wing kinematics from high speed video and processing the
measured data\cite{richter2012thesis}.

% TODO: Mention polynomial fitting then differentiation to get derivatives.

% Figure~\ref{fig:kinematics} provides sample force data and measured wing
% kinematics from one experiment.

@@

% TODO: Make sure to define all variables used in these tables.
% TODO: Figure out why we're calling it "U-squared".
\begin{table}[ht]
\centering
\begin{tabular}{|l|l|r|r|r|}
\hline
  {\bf Model} & {\bf Terms/Formula} & {\bf Size} & {\bf MAE (N)}\\
\hline
\(EQ _5\) & \(C_1RY_{CM}\dot{\psi}^2\ + C_2RX_{CM}\dot{\phi}\psi - C_3R\ddot{\theta}\) & 12 & 1.19\e{-3}\\
\(EQ _4\) & \(C_1RY_{CM}\dot{\psi}^2\cos\psi + C_2RX_{CM}\dot{\phi}\psi - C_3R\ddot{\theta}\) & 14 & 1.18\e{-3}\\
\(EQ _3\) & \(C_1RY_{CM}\dot{\psi}^2\cos(\psi-\psi^2) + C_2RX_{CM}\dot{\phi}\psi - C_3R\ddot{\theta}\) & 16 & 1.14\e{-3}\\
\(EQ _2\) & \(C_1RY_{CM}\dot{\psi}^2\cos\psi + C_2RX_{CM}\dot{\phi}\psi - C_3R\dot{\phi}\dot{\psi}\psi - C_4R\ddot{\theta}\) & 19 & 1.14\e{-3}\\
\(EQ _1\) & \(C_1RY_{CM}\dot{\psi}^2\cos\psi + C_2RX_{CM}\dot{\phi}\psi - C_3R\ddot{\theta}\dot{\phi}\psi - C_4R\dot{\phi}\dot{\psi}\psi - C_5R\ddot{\theta}\) & 24 & 1.12\e{-3}\\
\hline
\(U^2\) Planar 1 & \(L_{planar},  F_{inertial\:(pendulum\:only)}\) & 32 & 1.46\e{-3}\\
\(U^2\) Planar 2 & \(L_{planar}, F_{inertial}\) & 46 & 1.28\e{-3}\\
\(U^2\) Total & \(L_{trans}, F_{inertial}\) & 96 & 1.28\e{-3}\\
WW~\cite{whitney2010aeromechanics} & \(L_{trans}, AM_{trans}, AM_{rot}\) & 121 & 1.21\e{-3}\\
PW~\cite{pesavento2004falling} & \(L_{trans}, L_{rot}, AM_{trans}, AM_{trans-rot}\) & 130 & 1.20\e{-3}\\
\hline
\end{tabular}
\caption{\label{table:eqmodels}Comparison of data-driven models and analytical
  equations of lift.  The models are sorted by equation size, which is
  calculated as the sum of arithmetic and trigonometric operators required to
  compute a force prediction from kinematic and geometric data.  MAE reports
  average mean absolute error (in Newtons of vertical force) for the ten test
  experiments.}
\end{table}

@@

% TODO: Make sure the bibliography entries have the right elements and are capitalized properly.
\bibliographystyle{abbrv}
\bibliography{main}
